---
title: "Paper_01"
author: "JAMM"
date: "2022-08-04"
output: html_document
---

```{r setup, include=FALSE}
# Load libraries
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
p_load(dplyr, tidyverse,tibble,plyr,kableExtra,tictoc,purrr,ggplot2,
       fitdistrplus, plyr, knitr, scales)
```

# Load the Bayes and OLS

```{r, include = FALSE}
# Load needed data to get results
## Funds and Returns ####
RealReturns<- readRDS("RealReturns")
FundsToUse <- readRDS("Number_of_Fund") # Real Funds Numbers
colnames(FundsToUse)[1] <- c("Funds")

# Bayes ####
# We load the DBs and conver to numeric where necessary for the analysis
# Estimated Alphas IS (5 year period)
BayAlphaIS <- readRDS('Bayes_5_Year_Median_Alpha')
# Probabilities IS (5 year period)
BayProbIS <- readRDS('Bayes_5_Year_Prob')
# Estimated Alphas OOS (1 year period)
BayAlphaOOS <- readRDS('Bayes_1_Year_Median_Alpha')
# Probabilities OOS (1 year period)
BayProbOOS <- readRDS('Bayes_1_Year_Prob')

# OLS ####
OLSAlphaIS <- readRDS('OLS_Alphas_5_Year') 
OLSpValueIS <- readRDS('OLS_pValue_5_Year')
OLSAlphaOOS <- readRDS('OLS_Alphas_1_Year')
OLSpValueOOS <- readRDS('OLS_pValue_1_Year')
```

# Calculation of DFs

## Bayes Positive

```{r, include = FALSE}
# Bayes
## Bayes IS ####
# Funds detected in IS not free of survivor bias
BayIS_All90 <- lapply(2:44, function(x)
  (tibble(BayProbIS %>% dplyr::select(Funds,x) %>% 
            filter(.[[2]] >= 0.90))))

# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
IS_Bayes_Detected90 <- lapply(2:44, function(x)
    left_join(
      BayProbIS %>% dplyr::select(Funds, x) %>% 
        filter(!is.na(.[[2]]) & .[[2]] >= 0.90),
      BayAlphaIS %>% dplyr::select(Funds, x)
      , by = 'Funds'))

# The returns for the list above throughout each month
IS_Bayes_Detected_Rtns90 <- lapply(2:44, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] >= 0.90) %>% 
      dplyr::select(Funds),
    RealReturns %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
      
##  Bayes OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_Bayes_Detected90 <- lapply(2:43, function(x)
  left_join(
    BayProbOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] >= 0.90),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_Bayes_Detected_Rtns90 <- lapply(2:43, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] >= 0.90) %>% 
      dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
```

## OLS Positive

```{r, include = FALSE}
##  OLS IS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
OLSIS_All90 <-lapply(2:44, function(x)
  left_join(OLSAlphaIS %>% dplyr::select(1,x) %>% filter(.[[2]] > 0),
            OLSpValueIS %>% dplyr::select(1,x) %>% filter(.[[2]] <= 0.10),
            by = 'Funds') %>% filter(!is.na(.[[3]])))

# Funds detected in IS free of survivor bias
IS_OLS_Detected90 <- lapply(2:44, function(x) 
  left_join(
    OLSAlphaIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] >= 0.0),
    OLSpValueIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]))
    , by = 'Funds') %>% filter(.[[3]] <= 0.10))

# The returns for the list above throughout each month
IS_OLS_Detected_Rtns90 <- lapply(2:44, function(x) 
  left_join(
    IS_OLS_Detected90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav)%>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

##  OLS OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_OLS_Detected90 <- lapply(2:43, function(x) 
  inner_join(
    OLSAlphaOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] >= 0),
    OLSpValueOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_OLS_Detected_Rtns90 <- lapply(2:43, function(x) 
  left_join(
    OOS_OLS_Detected90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
```

## Bayes Negative

```{r, include = FALSE}
## Bayes IS ####
# Funds detected in IS not free of survivor bias
BayIS_All_neg90 <- lapply(2:44, function(x)
  (tibble(BayProbIS %>% dplyr::select(Funds,x) %>% 
            filter(.[[2]] <= 0.10))))

# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
IS_Bayes_Detected_neg90 <- lapply(2:44, function(x)
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10),
    BayAlphaIS %>% dplyr::select(Funds, x)
    , by = 'Funds'))

# The returns for the list above throughout each month
IS_Bayes_Detected_Rtns_neg90 <- lapply(2:44, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10) %>% 
      dplyr::select(Funds),
    RealReturns %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

##  Bayes OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_Bayes_Detected_neg90 <- lapply(2:43, function(x)
  left_join(
    BayProbOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_Bayes_Detected_Rtns_neg90 <- lapply(2:43, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10) %>% 
      dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

```

## OLS Negative

```{r, include = FALSE}
##  OLS IS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
OLSIS_All_neg90 <-lapply(2:44, function(x)
  left_join(OLSAlphaIS %>% dplyr::select(1,x) %>% filter(.[[2]] < 0),
            OLSpValueIS %>% dplyr::select(1,x) %>% filter(.[[2]] <= 0.10),
            by = 'Funds') %>% filter(!is.na(.[[3]])))

# Funds detected in IS free of survivor bias
IS_OLS_Detected_neg90 <- lapply(2:44, function(x) 
  left_join(
    OLSAlphaIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] < 0.0),
    OLSpValueIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]))
    , by = 'Funds') %>% filter(.[[3]] <= 0.10))

##  OLS OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_OLS_Detected_neg90 <- lapply(2:43, function(x) 
  inner_join(
    OLSAlphaOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] < 0),
    OLSpValueOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] <= 0.10)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_OLS_Detected_Rtns_neg90 <- lapply(2:43, function(x) 
  left_join(
    OOS_OLS_Detected_neg90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

# The returns for the list above throughout each month
IS_OLS_Detected_Rtns_neg90 <- lapply(2:44, function(x) 
  left_join(
    IS_OLS_Detected_neg90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav)%>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
```

## Bayes Zero

```{r, include = FALSE}
## Bayes IS ####
# Funds detected in IS not free of survivor bias
BayIS_All_zer90 <- lapply(2:44, function(x)
  (tibble(BayProbIS %>% dplyr::select(Funds,x) %>% 
            filter(.[[2]] > 0.10 & .[[2]] < 0.90))))

# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
IS_Bayes_Detected_zer90 <- lapply(2:44, function(x)
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] > 0.10 & .[[2]] < 0.90),
    BayAlphaIS %>% dplyr::select(Funds, x)
    , by = 'Funds'))

# The returns for the list above throughout each month
IS_Bayes_Detected_Rtns_zer90 <- lapply(2:44, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] > 0.10 & .[[2]] < 0.90) %>% 
      dplyr::select(Funds),
    RealReturns %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

##  Bayes OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_Bayes_Detected_zer90 <- lapply(2:43, function(x)
  left_join(
    BayProbOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] > 0.10 & .[[2]] < 0.90),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_Bayes_Detected_Rtns_zer90 <- lapply(2:43, function(x) 
  left_join(
    BayProbIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] > 0.10 & .[[2]] < 0.90) %>% 
      dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>% 
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
```

## OLS Zero

```{r, include = FALSE}
##  OLS IS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period IS
OLSIS_All_zer90 <-lapply(2:44, function(x)
  left_join(OLSAlphaIS %>% dplyr::select(1,x),
            OLSpValueIS %>% dplyr::select(1,x) %>% filter(.[[2]] > 0.10),
            by = 'Funds') %>% filter(!is.na(.[[3]])))

# Funds detected in IS free of survivor bias
IS_OLS_Detected_zer90 <- lapply(2:44, function(x) 
  left_join(
    OLSAlphaIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]])),
    OLSpValueIS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]))
    , by = 'Funds') %>% filter(.[[3]] > 0.10))

# The returns for the list above throughout each month
IS_OLS_Detected_Rtns_zer90 <- lapply(2:44, function(x) 
  left_join(
    IS_OLS_Detected_zer90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav)%>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)

##  OLS OOS ####
# One has a list per period with the detected funds in the 
# 5-year period, next period and t + 1 period OOS
OOS_OLS_Detected_zer90 <- lapply(2:43, function(x) 
  inner_join(
    OLSAlphaOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]])),
    OLSpValueOOS %>% dplyr::select(Funds, x) %>% 
      filter(!is.na(.[[2]]) & .[[2]] > 0.10)
    , by = 'Funds'))

# The returns for the list above throughout each month
OOS_OLS_Detected_Rtns_zer90 <- lapply(2:43, function(x) 
  left_join(
    OOS_OLS_Detected_zer90[[x-1]] %>% dplyr::select(Funds),
    RealReturns  %>% dplyr::select(Funds, returnrf, date, mtna, mnav) %>%
      filter(date >= '1979-12-01'), 
    by = 'Funds')
)
```

# Detection of funds

The next code output is to have the list of tables of the detection for each of the positive, negative and zero funds, according to the conditions written in the paper.

# Total of funds per period

```{r, echo = FALSE}
funds_per_year_90 <- sapply(2:ncol(BayAlphaIS), function(x) 
  nrow(BayAlphaIS %>% dplyr::select(x) %>% filter(!is.na(.))))
funds_per_year_90
funds_per_year_table_90 <- bind_cols(Year = 1979:2021, Funds = funds_per_year_90)
# write.table((funds_per_year_table_90),
#             file = 'Number_of_Funds_90.txt',sep = ' ', row.names = F, quote = F)
```

# Plot
``` {r, echo = FALSE}
# Number of funds per period (5-years)
# ggsave(filename = "Number_Funds_90.png",
ggplot(reshape2::melt(funds_per_year_table_90, id.var = "Year"),
       aes(Year,value,colour = variable)) +
  geom_line(aes(linetype=variable, group = variable)) +
  scale_linetype_manual("", values=c("solid", "dashed","solid", "dashed"),
                        labels = "Number of funds per year") +
  theme_classic() +
  labs(x = "Year", y = "Number of Funds") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.9, hjust=1.5))+
  scale_color_manual("",values = c("steelblue3","red2", "darkgreen","pink"),
                     labels = "Number of funds per year") +
  theme(legend.position = "bottom",legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11),legend.title=element_blank())
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')
```

# Detection
## Positive
```{r, echo = FALSE}
detection_positive90 <- bind_cols(
  Bayes = sapply(1:43, function(x)
    nrow(IS_Bayes_Detected90[[x]])),
  OLS = sapply(1:43, function(x) 
    nrow(IS_OLS_Detected90[[x]]))
)
detection_positive90
colMeans(detection_positive90)
```

## Negative
```{r, echo = FALSE}
detection_neg90 <- bind_cols(
  Bayes = sapply(1:43, function(x)
    nrow(IS_Bayes_Detected_neg90[[x]])),
  OLS = sapply(1:43, function(x) 
    nrow(IS_OLS_Detected_neg90[[x]]))
)
detection_positive90
colMeans(detection_positive90)
```

## Zero
```{r, echo = FALSE}
# Detected Funds
detection_zer_90 <- bind_cols(
  Bayes = funds_per_year_90 - detection_positive90$Bayes - detection_neg90$Bayes,
  OLS = funds_per_year_90 - detection_positive90$OLS - detection_neg90$OLS
)
detection_zer_90
colMeans(detection_zer_90)
```

### Final Table
``` {r, echo =FALSE}
# Detection Table ####
## Positive ####
detection_table90 <- bind_cols(
  paste0(1975:2017,rep('-'),1979:2021)[1:43],
  detection_positive90, detection_neg90, detection_zer_90
)
colnames(detection_table90)<- c("5-Year Period", 'BayesP','OLSP','BayesN','OLSN', 'ZeroB','ZeroOLS')
detection_table90
# write.table((detection_table90),
#             file = 'detection90.txt',sep = ',', row.names = F, quote = F)
```

### Prop of Tot
```{r, echo=FALSE}
# Proportion of detected funds out of the total number of funds in the period
# Bayes
final_table_Bayes_90 <- bind_cols(funds_per_year_table_90, Positive = detection_positive90$Bayes, Negative = detection_neg90$Bayes)
final_table_Bayes_90 <- final_table_Bayes_90 %>% mutate(Zero = Funds - Positive - Negative) %>% 
  mutate(Prop_Pos = Positive / Funds) %>% 
  mutate(Prop_Neg = Negative / Funds) %>% 
  mutate(Prop_Zero = Zero / Funds)
final_table_Bayes_90 %>% dplyr::select(Year, Prop_Pos, Prop_Neg, Prop_Zero)
## Save
# write.table((final_table_Bayes_90 %>% dplyr::select(Year, Prop_Pos, Prop_Neg, Prop_Zero)),
#             file = 'porportion_Bayes_Initial_90.txt',sep = ',', row.names = F, quote = F)
# OLS
final_table_OLS_90 <- bind_cols(funds_per_year_table_90, Positive = detection_positive90$OLS, Negative = detection_neg90$OLS)
final_table_OLS_90 <- final_table_OLS_90 %>% mutate(Zero = Funds - Positive - Negative) %>% 
  mutate(Prop_Pos = Positive / Funds) %>% 
  mutate(Prop_Neg = Negative / Funds) %>% 
  mutate(Prop_Zero = Zero / Funds)
final_table_OLS_90 %>% dplyr::select(Year, Prop_Pos, Prop_Neg, Prop_Zero)
# write.table((final_table_OLS_90 %>% dplyr::select(Year, Prop_Pos, Prop_Neg, Prop_Zero)),
#             file = 'porportion_OLS_Initial_90.txt',sep = ',', row.names = F, quote = F)
```
### Plot
```{r, echp = FALSE}
# Detection Plot ####
# ggsave(filename = "Detected_IS_90.png",
ggplot(reshape2::melt(detection_table90 %>% dplyr::select(1:5), id.var = "5-Year Period"),
       aes(`5-Year Period`,value,colour = variable)) +
  geom_line(aes(linetype=variable, group = variable)) +
  scale_linetype_manual("", values=c("solid", "dashed","solid", "dashed"),
                        labels = c("Bayes \n Positive Alpha", "OLS \n Positive Alpha",
                                   "Bayes \n Negative Alpha", "OLS \n Negative Alpha")) +
  theme_classic() +
  scale_y_continuous(trans='log10') +
  labs(x = "IS Period", y = "Positive alpha funds \n (logarithmic)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.9, hjust=1.5))+
  scale_color_manual("",values = c("steelblue3","red2", "darkgreen","pink"),
                     labels = c("Bayes \n Positive Alpha", "OLS \n Positive Alpha",
                                "Bayes \n Negative Alpha", "OLS \n Negative Alpha")) +
  theme(legend.position = "bottom",legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11),legend.title=element_blank())
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')

```

# Proportions
## Positive
```{r, echo = FALSE}
# IS Proportion skilled
proportion_IS_skilled_positive_90 <- bind_cols(
  Bayes = sapply(1:42, function(x) 
    nrow(inner_join(IS_Bayes_Detected90[[x]],
                    IS_Bayes_Detected90[[x+1]], 
                    by = 'Funds')) / nrow(IS_Bayes_Detected90[[x]])),
  OLS = sapply(1:42, function(x) 
    nrow(inner_join(IS_OLS_Detected90[[x]],
                    IS_OLS_Detected90[[x+1]],
                    by = 'Funds'))/nrow(IS_OLS_Detected90[[x]]))
)
proportion_IS_skilled_positive_90
colMeans(proportion_IS_skilled_positive_90, na.rm = T)
# t.test(proportion_IS_skilled_positive$Bayes, proportion_IS_skilled_positive$OLS)
# wilcox.test(proportion_IS_skilled_positive$Bayes, proportion_IS_skilled_positive$OLS)

# OOS Proportion skilled
# We find intersection from what we saw 5 years ago and what we 
# see the immediate next period
proportion_OOS_skilled_positive_90 <- bind_cols(
  Bayes = sapply(1:42, function(x) 
    nrow(inner_join(OOS_Bayes_Detected90[[x]],
                    IS_Bayes_Detected90[[x]], 
                    by = 'Funds')) / nrow(IS_Bayes_Detected90[[x]])),
  OLS = sapply(1:42, function(x) 
    nrow(inner_join(OOS_OLS_Detected90[[x]],
                    IS_OLS_Detected90[[x]],
                    by = 'Funds'))/nrow(IS_OLS_Detected90[[x]]))
)
proportion_OOS_skilled_positive_90
colMeans(proportion_OOS_skilled_positive_90,na.rm = T)
# Lack of recent positive alphas make the difference less significant
# t.test(proportion_OOS_skilled_positive$Bayes, proportion_OOS_skilled_positive$OLS)
# wilcox.test(proportion_OOS_skilled_positive$Bayes, proportion_OOS_skilled_positive$OLS)
```

## Negative
```{r, echo = FALSE}
# IS Proportion skilled
proportion_IS_skilled_neg_90 <- bind_cols(
  Bayes = sapply(1:42, function(x) 
    nrow(inner_join(IS_Bayes_Detected_neg90[[x]],
                    IS_Bayes_Detected_neg90[[x+1]], 
                    by = 'Funds')) / nrow(IS_Bayes_Detected_neg90[[x]])),
  OLS = sapply(1:42, function(x) 
    nrow(inner_join(IS_OLS_Detected_neg90[[x]],
                    IS_OLS_Detected_neg90[[x+1]],
                    by = 'Funds'))/nrow(IS_OLS_Detected_neg90[[x]]))
)
proportion_IS_skilled_neg_90
colMeans(proportion_IS_skilled_neg_90, na.rm = T)
# t.test(proportion_IS_skilled_neg$Bayes, proportion_IS_skilled_neg$OLS)
# wilcox.test(proportion_IS_skilled_neg$Bayes, proportion_IS_skilled_neg$OLS)

# OOS Proportion skilled
# We find intersection from what we saw 5 years ago and what we 
# see the immediate next period
proportion_OOS_skilled_neg_90 <- bind_cols(
  Bayes = sapply(1:42, function(x) 
    nrow(inner_join(OOS_Bayes_Detected_neg90[[x]],
                    IS_Bayes_Detected_neg90[[x]], 
                    by = 'Funds')) / nrow(IS_Bayes_Detected_neg90[[x]])),
  OLS = sapply(1:42, function(x) 
    nrow(inner_join(OOS_OLS_Detected_neg90[[x]],
                    IS_OLS_Detected_neg90[[x]],
                    by = 'Funds'))/nrow(IS_OLS_Detected_neg90[[x]]))
)
proportion_OOS_skilled_neg_90
colMeans(proportion_OOS_skilled_neg_90,na.rm = T)
# Lack of recent positive alphas make the difference less significant
# t.test(proportion_OOS_skilled_neg$Bayes, proportion_OOS_skilled_neg$OLS)
# wilcox.test(proportion_OOS_skilled_neg$Bayes, proportion_OOS_skilled_neg$OLS)
```

## Prop Tables
### IS
``` {r, echo = FALSE}
# Proportion IS Table ####
porportion_IS_table90 <- bind_cols(
  paste0(1976:2017,rep('-'),1980:2021)[1:42],
  percent(proportion_IS_skilled_positive_90$Bayes,accuracy = 0.01),
  percent(proportion_IS_skilled_positive_90$OLS, accuracy = 0.01),
  percent(proportion_IS_skilled_neg_90$Bayes,accuracy = 0.01),
  percent(proportion_IS_skilled_neg_90$OLS,accuracy = 0.01)
)
colnames(porportion_IS_table90) <- c("5-Year Period",'BayesP','OLSP', 'BayesN', 'OLSN')
porportion_IS_table90
## Save
# write.table((porportion_IS_table90),
#             file = 'porportion_IS_table90.txt',sep = ',', row.names = F, quote = F)

```
### OOS
```{r, echo = FALSE}
# Proportion OOS Table ####
proportion_OOS_skilled90 <- bind_cols(
  1980:2021,
  percent(proportion_OOS_skilled_positive_90$Bayes,accuracy = 0.01),
  percent(proportion_OOS_skilled_positive_90$OLS, accuracy = 0.01),
  percent(proportion_OOS_skilled_neg_90$Bayes,accuracy = 0.01),
  percent(proportion_OOS_skilled_neg_90$OLS, accuracy = 0.01)
)
colnames(proportion_OOS_skilled90) <- c("Periods",'BayesP','OLSP', 'BayesN', 'OLSN')
proportion_OOS_skilled90
## Save
# write.table((proportion_OOS_skilled90),
#             file = 'porportion_OOS_table90.txt',sep = ',', row.names = F, quote = F)
```
### PLOTS
``` {r, echo = FALSE}
data_prop_plot_90 <- bind_cols(
  Periods = 1980:2021,
  (proportion_OOS_skilled_positive_90$Bayes),
  (proportion_OOS_skilled_positive_90$OLS),
  (proportion_OOS_skilled_neg_90$Bayes),
  (proportion_OOS_skilled_neg_90$OLS)
)
## Positive
# ggsave(filename = "OOS_Prop_P_90.png",
ggplot(reshape2::melt(data_prop_plot_90[,1:3], id.var = "Periods"),
       aes(Periods,value,colour = variable)) +
  geom_line(aes(linetype=variable,group = variable))+
  scale_linetype_manual("", values=c("solid", "dashed", "solid", "dashed"),
                        labels = c("Bayes Positive Alpha","OLS Positive Alpha")) +
  theme_classic()+
  labs(x = "Out-of-Sample Years", y = "Proportion of \n positive alpha funds") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1.5))+
  scale_y_continuous(labels = scales::percent)+
  scale_color_manual("", values = c("steelblue3","red2"),
                     labels = c("Bayes Positive Alpha","OLS Positive Alpha")) +
  theme(legend.position = "bottom",legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11),legend.title=element_blank())
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')

## Negative
# ggsave(filename = "OOS_Prop_N_90.png",
ggplot(reshape2::melt(data_prop_plot_90[,c(1,4,5)], id.var = "Periods"),
       aes(Periods,value,colour = variable)) +
  geom_line(aes(linetype=variable,group = variable))+
  scale_linetype_manual("", values=c("solid", "dashed", "solid", "dashed"),
                        labels = c("Bayes Positive Alpha","OLS Positive Alpha")) +
  theme_classic()+
  labs(x = "Out-of-Sample Years", y = "Proportion of \n negative alpha funds") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1.5))+
  scale_y_continuous(labels = scales::percent)+
  scale_color_manual("", values = c("steelblue3","red2"),
                     labels = c("Bayes Negative Alpha","OLS Negative Alpha")) +
  theme(legend.position = "bottom",legend.text = element_text(size = 8),
        axis.text = element_text(size = 8),
        axis.title.x = element_text(size = 11),
        axis.title.y = element_text(size = 11),legend.title=element_blank())
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')


```


## Other Plots
```{r, echo = FALSE}
# IS ####
a <- melt(BayAlphaIS[,2:43])
head(a)
ggplot(a, aes(value, fill =  variable)) + geom_density()
ggplot(a, aes(value, color =  variable)) + 
  geom_density(alpha = 0.6) +
  theme_bw() +
  theme(legend.position = 'none') +
  xlim(-0.02,0.02)
# OOS ####
a2 <- melt(BayAlphaOOS[,2:43])
head(a)
ggplot(a, aes(value, fill =  variable)) + geom_density()
ggplot(a, aes(value, color =  variable)) + 
  geom_density(alpha = 0.6) +
  theme_bw() +
  theme(legend.position = 'none') +
  xlim(-0.05,0.05)


```

