---
title: "Untitled"
author: "JAMM"
date: "2022-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
p_load(dplyr, ggplot2, tidyquant, reshape2, tidyr, tidyquant)
# Bayes ####
# We load the DBs and conver to numeric where necessary for the analysis
# Estimated Alphas IS (5 year period)
BayAlphaIS <- readRDS('Bayes_5_Year_Median_Alpha')
# Probabilities IS (5 year period)
BayProbIS <- readRDS('Bayes_5_Year_Prob')
# Estimated Alphas OOS (1 year period)
BayAlphaOOS <- readRDS('Bayes_1_Year_Median_Alpha')
# Probabilities OOS (1 year period)
BayProbOOS <- readRDS('Bayes_1_Year_Prob')
# Returns ####
RealReturns<- readRDS("RealReturns")

```
# Alpha Analysis
For each period in the detection period, we create an EW portfolio of the alphas of the funds selected. Hold it for a year and compare the average of the portfolio's alpha between positive, negative and zero alpha. 

```{r, echo = FALSE, message =FALSE}
# List of ALPHA portfolios by period 
## POSITIVE ####
IS_to_1_90 <- lapply(2:43, function(x)
  left_join(
    left_join(
      left_join(
        BayProbIS %>% dplyr::select(Funds, x) %>% 
          filter(!is.na(.[[2]]) & .[[2]] >= 0.90),
        BayAlphaIS %>% dplyr::select(Funds, x)
        , by = 'Funds'),
      BayProbOOS %>% dplyr::select(Funds,x)
    , by = 'Funds'),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    ,by = 'Funds') %>% filter(!is.na(.[[4]])))
## NEGATIVE ####
IS_to_1_neg_90 <- lapply(2:43, function(x)
  left_join(
    left_join(
      left_join(
        BayProbIS %>% dplyr::select(Funds, x) %>% 
          filter(!is.na(.[[2]]) & .[[2]] <= 0.10),
        BayAlphaIS %>% dplyr::select(Funds, x)
        , by = 'Funds'),
      BayProbOOS %>% dplyr::select(Funds,x)
      , by = 'Funds'),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    ,by = 'Funds') %>% filter(!is.na(.[[4]])))

## ZERO  ####
IS_to_1_zer_90 <- lapply(2:43, function(x)
  left_join(
    left_join(
      left_join(
        BayProbIS %>% dplyr::select(Funds, x) %>% 
          filter(!is.na(.[[2]]) & .[[2]] > 0.10 & .[[2]] < 0.90),
        BayAlphaIS %>% dplyr::select(Funds, x)
        , by = 'Funds'),
      BayProbOOS %>% dplyr::select(Funds,x)
      , by = 'Funds'),
    BayAlphaOOS %>% dplyr::select(Funds, x)
    ,by = 'Funds') %>% filter(!is.na(.[[4]])))
```

```{r, echo = FALSE, warning = FALSE}
# We bind columns of results in the following way. First the years. Second the average column of the positive alphas the year after
# Examples to run before
# colMeans(IS_to_1_90[[7]] %>% dplyr::select(3,5))
# colMeans(IS_to_1_neg_90[[12]] %>% dplyr::select(3,5))
# colMeans(IS_to_1_zer_90[[12]] %>% dplyr::select(3,5))

alphas_t_t1_90 <- bind_cols(
  Year = 1980:2021,
  EW_Alpha_t1_Pos_90 = t(sapply(1:42, function(x)
    colMeans(IS_to_1_90[[x]] %>% dplyr::select(3,5))
  ))[,2],
  EW_Alpha_t1_Neg_90 = t(sapply(1:42, function(x)
    colMeans(IS_to_1_neg_90[[x]] %>% dplyr::select(3,5))
  ))[,2],
  EW_Alpha_t1_Zer_90 = t(sapply(1:42, function(x)
    colMeans(IS_to_1_zer_90[[x]] %>% dplyr::select(3,5))
  ))[,2]
)
colnames(alphas_t_t1_90) <- c('Year','Pos.Alph.t1','Neg.Alph.t1','Zer.Alph.t1')
# Store Table
# write.table(alphas_t_t1_90,
#             file = 'alphas_t_t1_90.txt',sep = ',', row.names = F, quote = F)
alphas_t_t1_90 %>% print(n = Inf)

# Plot ####
# ggsave(filename = "Alpha_Portfolios_Returns_90.png",
# ggplot(melt(alphas_t_t1_90, 
#      id.vars = 'Year'),aes(x = Year, y = value, colour = factor(variable))) +
#   geom_line() +
#   ylab('Average end of \n Period Alpha') +
#   theme_classic() + 
#   scale_color_manual("",values = c("steelblue3","red2", 'darkgreen'),
#                      labels = c('Positive Alpha', 'Negative Alpha', 'Zero Alpha')) +
#   theme(legend.position="bottom", legend.text=element_text(size=9))
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')

```

# Portfolio of returns
For each period in the detection period, we create an EW portfolio of the returns of the funds selected. Hold it for a year and compare the average of the portfolio's return between positive, negative and zero alpha. 

```{r, echo = FALSE}
# List of RETURN portfolios by period 
## POSITIVE ####
ret_portf_pos_90 <- lapply(1:42, function(x) 
  left_join(
      IS_to_1_90[[x]] %>% dplyr::select(Funds),
    RealReturns %>% 
      dplyr::select(Funds, returnrf, date) %>% 
      filter(date >= paste(1979+x,'-01-01',sep = '') & 
               date <= paste(1979+x,'-12-31',sep = '')),
    by = 'Funds')
  )
## NEGATIVE ####
ret_portf_neg_90 <- lapply(1:42, function(x) 
  left_join(
      IS_to_1_neg_90[[x]] %>% dplyr::select(Funds),
    RealReturns %>% 
      dplyr::select(Funds, returnrf, date) %>% 
      filter(date >= paste(1979+x,'-01-01',sep = '') & 
               date <= paste(1979+x,'-12-31',sep = '')),
    by = 'Funds')
)
## ZERO ####
ret_portf_zer_90 <- lapply(1:42, function(x) 
  left_join(
      IS_to_1_zer_90[[x]] %>% dplyr::select(Funds),
    RealReturns %>% 
      dplyr::select(Funds, returnrf, date) %>% 
      filter(date >= paste(1979+x,'-01-01',sep = '') & 
               date <= paste(1979+x,'-12-31',sep = '')),
    by = 'Funds')
)
```
# SP500
Code chunk to load and prepare the SP500 data to add as comparison benchmark for the rest.
```{r, echo=FALSE}
sp500 <- as_tibble(read.csv('sp500_monthly.csv')) %>% dplyr::select(caldt, sprtrn) %>% dplyr::rename(date = caldt )
sp500$date <- as.Date(as.character(sp500$date), format = "%Y%m%d")
sp500 <- distinct(right_join(sp500,RealReturns %>% dplyr::select(date, rf),by = 'date')) %>% mutate(sprtrnRf = sprtrn - rf)
sp500_ret <- lapply(1:42, function(x)
      sp500 %>%
        filter(date >= paste(1979+x,'-01-01',sep = '') &
                 date <= paste(1979+x,'-12-31',sep = '')))
```

```{r}
## Table of columns  ####
# Example with a year
# colMeans(ret_portf_pos_90[[7]] %>% group_by(Funds) %>% summarise(Suma = sum(returnrf)) %>% dplyr::select(Suma))

returns_portf_90 <- 
  bind_cols(
    Year = 1980:2021,
    as_tibble(sapply(
      1:42, function(x)
        colMeans(ret_portf_pos_90[[x]] %>% group_by(Funds) %>% dplyr::summarise(Suma = sum(returnrf)) %>% dplyr::select(Suma)))),
    as_tibble(sapply(
      1:42, function(x)
        colMeans(ret_portf_neg_90[[x]] %>% group_by(Funds) %>% dplyr::summarise(Suma = sum(returnrf)) %>% dplyr::select(Suma)))),
    as_tibble(sapply(
      1:42, function(x)
        colMeans(ret_portf_zer_90[[x]] %>% group_by(Funds) %>% dplyr::summarise(Suma = sum(returnrf)) %>% dplyr::select(Suma))))
    , 
as_tibble(sapply(
  1:42, function(x)
        colMeans(sp500_ret[[x]] %>% dplyr::summarise(Suma = sum(sprtrnRf)) %>% dplyr::select(Suma))))
    )
colnames(returns_portf_90) <- c('Year', 'Pos.Alph.Ret.t1','Neg.Alph.Ret.t1','Zer.Alph.Ret.t1', 'S&P500')
# write.table(returns_portf_90,
#             file = 'returns_portf_90.txt',sep = ',', row.names = F, quote = F)
returns_portf_90 %>% print(n = Inf)
```
## Figure with returns per alpha
```{r, echo = FALSE}
# Make sure to add the column of SP500 as cbind
# ggsave(filename = "returns_portf_90.png",
ggplot(melt(bind_cols(returns_portf_90 %>% dplyr::select(Year, 2:5)), 
            id.vars = 'Year'),aes(x = Year, y = value, colour = factor(variable))) +
  geom_line() +
  ylab('Return of Portfolios \n (One Holding Period)') +
  theme_minimal() + 
  scale_y_continuous(labels = scales::percent) +
  scale_color_manual("",values = c("steelblue3","red2", 'darkgreen', 'orange'),
                     labels = c('Positive Alpha', 'Negative Alpha', 'Zero Alpha', 'S&P500')) +
  geom_hline(yintercept=0, color = "black") +
  theme(legend.position="bottom", legend.text=element_text(size=9))
# ,width = 10, height = 4, dpi = 300, units = "in", device='png')
```


